### 2023-02-23 README.qmd
updated domain

[![Stable](https://img.shields.io/badge/docs-stable-blue.svg)](https://pat-alt.github.io/AlgorithmicRecourseDynamics.jl/stable) 
[![Dev](https://img.shields.io/badge/docs-dev-blue.svg)](https://pat-alt.github.io/AlgorithmicRecourseDynamics.jl/dev) 
[![Build Status](https://github.com/pat-alt/AlgorithmicRecourseDynamics.jl/actions/workflows/CI.yml/badge.svg?branch=main)](https://github.com/pat-alt/AlgorithmicRecourseDynamics.jl/actions/workflows/CI.yml?query=branch%3Amain) 
[![Coverage](https://codecov.io/gh/pat-alt/AlgorithmicRecourseDynamics.jl/branch/main/graph/badge.svg)](https://codecov.io/gh/pat-alt/AlgorithmicRecourseDynamics.jl) 
[![Code Style: Blue](https://img.shields.io/badge/code%20style-blue-4495d1.svg)](https://github.com/invenia/BlueStyle) 
[![ColPrac: Contributor’s Guide on Collaborative Practices for Community Packages](https://img.shields.io/badge/ColPrac-Contributor's%20Guide-blueviolet.png)](https://github.com/SciML/ColPrac) 
[![Twitter Badge](https://img.shields.io/twitter/url/https/twitter.com/paltmey.svg?style=social&label=Follow%20%40paltmey)](https://twitter.com/paltmey)

>>>>

[![Stable](https://img.shields.io/badge/docs-stable-blue.svg)](https://juliatrustworthyai.github.io/AlgorithmicRecourseDynamics.jl/stable) 
[![Dev](https://img.shields.io/badge/docs-dev-blue.svg)](https://juliatrustworthyai.github.io/AlgorithmicRecourseDynamics.jl/dev) 
[![Build Status](https://github.com/juliatrustworthyai/AlgorithmicRecourseDynamics.jl/actions/workflows/CI.yml/badge.svg?branch=main)](https://github.com/juliatrustworthyai/AlgorithmicRecourseDynamics.jl/actions/workflows/CI.yml?query=branch%3Amain) 
[![Coverage](https://codecov.io/gh/juliatrustworthyai/AlgorithmicRecourseDynamics.jl/branch/main/graph/badge.svg)](https://codecov.io/gh/juliatrustworthyai/AlgorithmicRecourseDynamics.jl) 
[![Code Style: Blue](https://img.shields.io/badge/code%20style-blue-4495d1.svg)](https://github.com/invenia/BlueStyle) 
[![ColPrac: Contributor’s Guide on Collaborative Practices for Community Packages](https://img.shields.io/badge/ColPrac-Contributor's%20Guide-blueviolet.png)](https://github.com/SciML/ColPrac) 
[![Twitter Badge](https://img.shields.io/twitter/url/https/twitter.com/paltmey.svg?style=social&label=Follow%20%40paltmey)](https://twitter.com/paltmey)

### 2023-02-23 docs/src/_intro.qmd
updated domain

`AlgorithmicRecourseDynamics.jl` is a small package for modeling Algorithmic Recourse Dynamics. It builds on `CounterfactualExplanations`, a package for generating counterfactual explanations.

## Basic Usage

@@

## Related Research Paper 📝

The package was developed for a research project that investigates the dynamics of various counterfactual generators. You can find the details [here](https://github.com/pat-alt/endogenous-macrodynamics-in-algorithmic-recourse).

>>>>

`AlgorithmicRecourseDynamics.jl` is a small package for modelling Algorithmic Recourse Dynamics that was developed as part of a research paper by @altmeyer2023endogenous. It builds on `CounterfactualExplanations`, a package for generating counterfactual explanations.

## 🔍 Basic Usage

@@

## 📝 Related Research Paper

The research paper by @altmeyer2023endogenous investigates the dynamics of various counterfactual generators. You can find the details [here](https://github.com/pat-alt/endogenous-macrodynamics-in-algorithmic-recourse).

## 🎓 References
